### 2012-09-04 sections/introduction.tex
* added survery paper introduction blurb * filter comparison graph changed to flowy 2.0 vs nfql

A survey by Sperotto \textit{et al.} \cite{sperotto:2010} gives an overview of
how network flow analysis can be used to detect Denial of Service attacks,
scans probing target systems and the target discovery phase of worms. In
addition, a survey by Callado \textit{et al.} \cite{callado:2009} also lists
behaviour analysis of Internet backbone traffic and general anomaly detection.

Understanding intricate traffic patterns require sophisticated flow analysis
tools that can mine flow records for such a usage.  Unfortunately current
tools fail to deliver owing to their language design and simplistic filtering
methods.  We recently proposed a flow query language design
\cite{vmarinov:2009} that aims to cater to such needs.  It can process
flow records, aggregate them into groups, apply absolute (or relative) filters
and invoke Allen interval algebra rules \cite{fallen:1983}. The applicability
of the language can be seen from \cite{vperelman:2011} where the authors
formulate flow queries to identify flow signatures of popular applications.

>>>>

The wide applicability of this approach is easily seen from the pervasive use
of flow records for a vibrant set of network analysis applications. For
instance, a survey by Sperotto \textit{et al.} \cite{sperotto:2010} gives an
overview of how network flow analysis can be used to detect Denial of Service
attacks, scan probing target systems and the target discovery phase of worms.
In addition, a survey by Callado \textit{et al.} \cite{callado:2009} also
lists behaviour analysis of Internet backbone traffic and general anomaly
detection.

Understanding intricate traffic patterns require sophisticated flow analysis
tools that can mine flow records for such a usage.  Unfortunately current
tools fail to deliver owing to their language design and simplistic filtering
methods.  We recently proposed a flow query language design
\cite{vmarinov:2009} that aims to cater to such needs.  It can process
flow records, aggregate them into groups, apply absolute (or relative) filters
and invoke Allen interval algebra rules \cite{fallen:1983}. The expressiveness
of the language can be seen from \cite{vperelman:2011} where the authors
formulate flow queries to identify flow signatures of popular applications.
